On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] - WIP

\section{Example of sets with many common points that canot be merged}

@@

TODO: 11_14450_1_8693fad981c82dc92d7c9365bcb9945e

@@

@@

TODO: 8_2535_1_d680ff2d172ebe40250a54ca9419af34

>>>>

Taking

\section{Example of sets with many common points that cannot be merged}

@@

TODO: 11\_14450\_1\_8693fad981c82dc92d7c9365bcb9945e

@@

\section{Arrow-like integral point sets with one axis of symmetry}

на каждое такое множество: исходный вариант, все этапы растращаивания с коэффициентом растаращивания и пояснением, кто из кого.

@@

TODO: 8\_2535\_1\_d680ff2d172ebe40250a54ca9419af34
